---
title: "Project R Markdown"
author: "Han Xu"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#| include: FALSE
```


```{r, load-data}
here::i_am("report_diamond_prize.Rmd")
data <- readRDS(
  file = here::here("output/data_clean.rds")
)
```


This dataset contains `r nrow(data)` round-cut diamonds with their prices and characteristics, such as carat, cut, color, clarity, depth, table, x, y, z. Here, x, y, z columns are diamond measurements which represent the length, width, and depth of the diamond, separately. Most variables in the dataset are numeric, while other variables cut, color, and clarity are ordered factor variables with different levels.

The goal of this subject is to investigate the association between the price and characteristics for each diamond such as the analysis of relationship between the quality, size, and size of the table facet for each diamond and their prices.


# Descriptive Analysis

## Tabular analysis

Basic information about size, quality, size of the table facet and price of the `r nrow(data)` diamonds from the Diamond_Price database are displayed in the table below.

```{r, table1}
table_one <- readRDS(
  file = here::here("output/table_one.rds")
)
table_one

```



## Graphical analysis


Below we report a scatter plot of prices of diamonds as a function of their sizes (unit: carat). 


```{r, plot-data}
#| fig.align = "center",
#| out.width = "800px"
knitr::include_graphics(
  here::here("output/scatterplot.png")
)
```

